---
title: "Take-home Exercise 2"
author: "Xu Qianqian"
date: "March 6, 2026"
date-modified: "last-modified"
execute: 
  eval: true
  echo: true
  warning: false
  freeze: true
---

# Predictive Modelling

## 1 Overview

This project aims to develop a robust predictive model to identify customer churn within a Colombian fintech environment. Using the **COFINFAD** dataset, which tracks the behavior of 48,723 customers over the 2023 calendar year, the analysis bridges the gap between customer sentiment and actual transactional behavior. By converting over 3.1 million raw transaction logs into actionable behavioral metrics, the project provides a data-driven strategy for proactive customer retention.

## 2 Install and Load Packages

In this project, we utilize thirteen R packages to facilitate data import, manipulation, and advanced visualization:

-   **`tidyverse`**: A collection of fundamental R packages designed for data science, covering everything from data cleaning to creating static statistical graphs.

-   **`naniar`**: Provides a suite of functions to tidy, visualize, and analyze **missing data** (NAs)

-   **`skimr`**: A tool for **quick data assessment**. It produces a "skim" of a dataframe, providing summary statistics (mean, SD, quantiles) and tiny inline histograms (sparklines) for a fast overview of distributions.

-   **`knitr`**: The engine behind **dynamic report generation** in R. It integrates R code into Markdown, LaTeX, or HTML documents, allowing you to "knit" your analysis into a finished report.

-   **`dplyr`**: It's the package for **filtering, selecting, mutating, and summarizing** dataframes using a clean, readable syntax.

-   **`kableExtra`**: An extension for `knitr::kable()` that provides advanced styling options for **HTML and PDF tables**, such as striped rows, hover effects, and complex headers.

-   **`patchwork`**: Makes **combining multiple ggplots** incredibly simple.

-   **`corrplot`**: A graphical display of a **correlation matrix**. It helps you quickly identify patterns and strengths of relationships between variables using colors and shapes.

-   **`tidymodels`**: A "meta-package" (like the tidyverse) designed for **modeling and machine learning**. It provides a consistent framework for preprocessing, training, and validating models.

-   **`ranger`**: A fast implementation of **Random Forests**. It is highly memory-efficient and particularly well-suited for high-dimensional data.

-   **`xgboost`**: An interface for **Extreme Gradient Boosting**. It’s a powerful, scalable library used for gradient-boosted decision trees, often favored in data science competitions for its speed and performance.

-   **`vip`**: Stands for **Variable Importance Plots**. It extracts and visualizes the importance of features in various machine learning models, helping you understand which variables are driving your model's predictions.

-   **`car`**: provides advanced statistical tests and diagnostic tools—such as the `vif()` function—to evaluate, troubleshoot, and refine regression models.

```{r}
pacman::p_load(tidyverse, naniar, skimr, knitr, dplyr,kableExtra, patchwork, corrplot, tidymodels,ranger, xgboost,vip,car)
```

## 3 Data Preparation

### 3.1 The Data

This project analyzes the [Colombian Fintech Financial Analytics Dataset](https://data.mendeley.com/datasets/mhb4zn3258/1) (COFINFAD). The dataset contains behavioral and transactional records for 48,723 customers, collected over a 12-month period from January 4 to December 29, 2023. Comprising over 3.1 million individual transactions, the data is designed to support research on customer retention, financial behavior, and digital service adoption in emerging Latin American markets.

The dataset consists of two CSV files:

-   **`transactions_data.csv`**: Transaction-level data (3,159,157 rows), where each row represents a single transaction.

-   **`customer_data.csv`**: Customer-level data (48,723 rows), including demographics, product portfolios, satisfaction metrics, and aggregated behavioral features.

### 3.2 Import Data

The following code chunk utilizes the **`read_csv()`** function from the **`readr`** package (part of the **tidyverse**) to import the datasets into the R environment.

```{r}
customer_data <- read_csv("data/customer_data.csv")
transactions_data <- read_csv("data/transactions_data.csv")
```

### 3.3 Preparing the Data

#### 3.3.1 Check Missing Values

```{r}
# Visualize missingness in customer data
gg_miss_var(customer_data)
```

In the customer dataset ($N = 48,723$), missing values are limited to `complaint_topics` (49.97%), `credit_utilization_ratio` (37.48%), and `feature_requests` (33.07%). These gaps are structural, occurring when a product or interaction is not applicable to the customer. Categorical missing values were imputed as 'None' or 'No Interaction'. For `credit_utilization_ratio`, NAs were filled with 0.

```{r}
customer_data_clean <- customer_data %>%
  mutate(
    # 1. Impute numerical data with 0 
    credit_utilization_ratio = replace_na(credit_utilization_ratio, 0),
    
    # 2. Impute categorical data with 'None' and 'No Interaction'
    complaint_topics = replace_na(complaint_topics, "None"),
    feature_requests = replace_na(feature_requests, "No Interaction"),
  )
```

```{r}
# Visualize missingness in transaction data
gg_miss_var(transactions_data)
```

All transaction-level variables are complete.

#### 3.3.2 Data Wrangling

##### 3.3.2.1 Recency, Frequency, and Monetary

To enhance the predictive power of the model, I will perform feature engineering on the `transactions_data.csv` to derive the **RFM** (Recency, Frequency, and Monetary) metrics for each of the 48,723 customers. These features are essential for capturing dynamic behavioral patterns that static demographic data may miss.

-   **Recency**: Calculated as the number of days between the customer's last transaction and the reference date of **December 30, 2023**.

-   **Frequency**: The total number of transactions recorded for each customer throughout the 12-month period.

-   **Monetary**: The total value of all transactions in Colombian Pesos (COP) for each individual customer.

By aggregating over 3.1 million transaction-level rows into these three customer-level dimensions, I can better identify high-value loyalists and distinguish them from at-risk users, providing a more robust foundation for churn prediction.

```{r}
# Set the reference date (one day after the last transaction in the dataset)
reference_date <- as.Date("2023-12-30")

# Calculate RFM metrics from transactions_data
rfm_features <- transactions_data %>%
  # Ensure the date column is in the correct Date format
  mutate(date = as.Date(date)) %>%
  group_by(customer_id) %>%
  summarise(
    # Recency: Days since the last transaction
    recency = as.numeric(reference_date - max(date)),
    
    # Frequency: Total count of transactions
    frequency = n(),
    
    # Monetary: Total sum of transaction amounts (in COP)
    monetary = sum(amount, na.rm = TRUE)
  )
```

##### 3.3.2.2 Merge RFM features with cleaned customer dataset

```{r}
# Merge RFM features with your cleaned customer dataset
customer_data_final <- customer_data_clean %>%
  left_join(rfm_features, by = "customer_id")
```

```{r}
# Visualize missingness in customer data
gg_miss_var(customer_data_final)
```

Every customer has a Recency, Frequency, and Monetary value.

##### 3.3.2.3 Statistical Summary of Data

```{r}
customer_data_final %>% 
  skim()
```

## 4 Analytical Workflow

The analytical workflow follows a systematic pipeline: initial **feature engineering** and **variable selection** to refine the high-dimensional dataset, followed by **univariate distribution analysis** to identify outliers. A **correlation matrix** is then utilized to detect initial pairwise multi-collinearity among the behavioral metrics. The data is subsequently partitioned through **random sampling** into training and testing sets. Finally, a **Variance Inflation Factor (VIF)** assessment is applied strictly to the training data to detect and eliminate any remaining multivariate collinearity before the **predictive models** are developed.

### 4.1 Feature Engineering and Variable Selection

To enhance model parsimony and mitigate the risks associated with high cardinality, categorical variables—specifically **location**, **occupation**, and **feature_requests**—were subjected to frequency-based lumping. Utilizing the `fct_lump_n` function, the feature space for each variable was condensed to preserve only the five most frequent levels, with all remaining infrequent categories consolidated into a standardized 'Other' designation.

```{r}
# Applying lumping to location, occupation, and feature_requests
modeling_data <- customer_data_final %>%
  mutate(
    # Preserve top 5 most frequent locations
    location = fct_lump_n(as.factor(location), n = 5, other_level = "Other"),
    
    # Preserve top 5 most frequent occupations
    occupation = fct_lump_n(as.factor(occupation), n = 5, other_level = "Other"),
    
    # Preserve top 5 feature requests
    feature_requests = fct_lump_n(as.factor(feature_requests), n = 5, other_level = "Other")
  )
```

To account for the duration of the customer relationship, a **Tenure** variable was engineered by calculating the chronological distance between each customer's `first_transaction_date` and the study's reference date of December 30, 2023. In contrast to the provided `customer_tenure` variable, which is measured in months, this daily calculation offers a high-granularity perspective on the customer lifecycle. This enables the model to more accurately identify churn risks within critical windows, such as the early onboarding phase or the transition into long-term loyalty."

```{r}
# Reference date based on the 2023 dataset cutoff
ref_date <- as.Date("2023-12-30")

modeling_data <- modeling_data %>%
  mutate(
    # Ensure first_transaction_date is in Date format
    first_transaction_date = as.Date(first_transaction_date),
    
    # Calculate Tenure in days
    tenure = as.numeric(ref_date - first_transaction_date)
  )
```

Prior to model training, a rigorous feature selection process was conducted to ensure model parsimony and prevent multicollinearity. The following table details the variables excluded from the final dataset, along with the specific technical or behavioral justification for their removal.

```{r}
#| label: tbl-excluded
#| tbl-cap: "Summary of Excluded Variables and Rationalization"
#| code-fold: true
#| code-summary: "Show the R code used to generate this table"

excluded_vars <- data.frame(
  Variable = c(
    "customer_id", 
    "last_tx / last_transaction_date", 
    "first_tx / first_transaction_date",
    "last_survey_date",
    "satisfaction_score",
    "avg_tx_value",
    "monthly_transaction_count",
    "average_transaction_value",
    "tx_count",
    "total_tx_volume",
    "total_transaction_volume",
    "transaction_frequency",
    "avg_daily_transactions",
    "customer_tenure",
    "clv_segment"
  ),
  Reason_for_Exclusion = c(
    "Zero predictive power; random identifier with no relationship to financial behavior.",
    "Redundant; information captured by the engineered 'Recency' feature.",
    "Redundant; information captured by the engineered 'Tenure' feature.",
    "Sentiment signal is better captured by satisfaction pillars or NPS; dates are less predictive than scores.",
    "Excluded to prioritize model interpretability; specific pillars (base, tx, product) provide more actionable insights.",
    "High multicollinearity with total_tx_volume.",
    "High multicollinearity with tx_count.",
    "Redundant; mathematically derived from monetary and frequency.",
    "Redundant; information captured by the engineered 'frequency' feature.",
    "Redundant; information captured by the engineered 'monetary' feature.",
    "Data inconsistency; shares a definition with total_tx_volume but contains significant system noise.",
    "High correlation with frequency.",
    "Perfectly correlated with frequency (mathematical derivative).",
    "Redundant; information captured by the higher-granularity 'Tenure' (days) feature.",
    "Categorical derivative of customer_lifetime_value; removed to preserve raw numeric granularity for the model."
  )
)

# Render the table
library(kableExtra)
kable(excluded_vars, 
      col.names = c("Variable", "Rationale for Exclusion")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "35em")
```

```{r}
# Finalizing the modeling dataset by excluding 17 redundant or low-predictive variables
modeling_data <- modeling_data %>%
  select(
    -customer_id,
    -last_tx, -last_transaction_date,
    -first_tx, -first_transaction_date,
    -last_survey_date,
    -satisfaction_score,            
    -avg_tx_value,
    -monthly_transaction_count,
    -average_transaction_value,
    -tx_count,
    -total_tx_volume,
    -total_transaction_volume,
    -transaction_frequency,
    -avg_daily_transactions,
    -customer_tenure,
    -clv_segment
  )
```

### 4.2 Univariate distribution Analysis

#### 4.2.1 Distribution of Target Variable

::: panel-tabset
## Plot

```{r, echo=FALSE}
ggplot(modeling_data, aes(x = churn_probability)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "skyblue", color = "white") +
  geom_density(alpha = 0.2, fill = "blue") +
  theme_minimal() +
  labs(
    title = "Univariate Distribution of Churn Probability",
    subtitle = "Understanding the baseline risk across the customer base",
    x = "Churn Probability (0 to 1)",
    y = "Density"
  )
```

## Code

```{r, eval=FALSE}
ggplot(modeling_data, aes(x = churn_probability)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "skyblue", color = "white") +
  geom_density(alpha = 0.2, fill = "blue") +
  theme_minimal() +
  labs(
    title = "Univariate Distribution of Churn Probability",
    subtitle = "Understanding the baseline risk across the customer base",
    x = "Churn Probability (0 to 1)",
    y = "Density"
  )
```
:::

```{r}
# Calculate specific risk tiers
risk_tiers <- quantile(modeling_data$churn_probability, probs = c(0.75, 0.90, 0.99))
print(risk_tiers)
```

The distribution of `churn_probability` is notably compressed, with a maximum value of **0.5006**. Because the vast majority of the population falls below the traditional **0.50** classification threshold, a standard binary approach would result in significant 'under-counting' of at-risk individuals. To address this, a **Relative Risk Framework** was adopted. The **75th percentile (0.3927)** was used to identify the transition into 'Medium Risk,' while the **90th percentile (0.4200)** was established as the operational threshold for 'High Risk' classification. This approach ensures the model identifies the most vulnerable **10%** of the customer base, providing actionable targets for the bank’s retention strategies by focusing on the highest relative risk.

```{r}
# Defining Risk Tiers based on calculated percentiles
modeling_data <- modeling_data %>%
  mutate(risk_group = case_when(
    churn_probability >= 0.4200 ~ "High Risk (>90th)",
    churn_probability >= 0.3927 ~ "Medium Risk (75th-90th)",
    TRUE ~ "Standard (<75th)"
  )) %>%
  # Ensuring factor levels are ordered for logical plotting
  mutate(risk_group = factor(risk_group, 
                             levels = c("Standard (<75th)", 
                                        "Medium Risk (75th-90th)", 
                                        "High Risk (>90th)")))
```

#### 4.2.2 Distribution of Numerical Variables

::: panel-tabset
## Plot

```{r, echo=FALSE}
#| fig-width: 14
#| fig-height: 18
#| label: fig-outlier-detection
#| fig-cap: "Outlier detection for all numerical features"


# Identify all numeric variables
numeric_cols <- modeling_data %>% 
  select(where(is.numeric)) %>% 
  colnames()

# Reshape data for a facet-grid boxplot
modeling_data %>%
  select(all_of(numeric_cols)) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  ggplot(aes(x = variable, y = value)) +
  geom_boxplot(fill = "steelblue", outlier.color = "red", outlier.shape = 1) +
  facet_wrap(~variable, scales = "free") + # 'free' is key because scales differ
  theme_minimal() +
  labs(title = "Outlier Detection Across Numerical Variables",
       subtitle = "Red dots indicate potential outliers beyond 1.5 * IQR") +
  theme(axis.text.x = element_blank()) 
```

## Code

```{r, eval=FALSE}

# Identify all numeric variables
numeric_cols <- modeling_data %>% 
  select(where(is.numeric)) %>% 
  colnames()

# Reshape data for a facet-grid boxplot
modeling_data %>%
  select(all_of(numeric_cols)) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  ggplot(aes(x = variable, y = value)) +
  geom_boxplot(fill = "steelblue", outlier.color = "red", outlier.shape = 1) +
  facet_wrap(~variable, scales = "free") + # 'free' is key because scales differ
  theme_minimal() +
  labs(title = "Outlier Detection Across Numerical Variables",
       subtitle = "Red dots indicate potential outliers beyond 1.5 * IQR") +
  theme(axis.text.x = element_blank()) 
```
:::

To balance model stability with data preservation, **Winsorization** was applied to the behavioral features **monetary**, **frequency**, and **customer_lifetime_value**. Rather than excluding these high-value data points, extreme outliers were capped at the **99th percentile**. This approach mitigates the influence of extreme variance on tree-splitting algorithms while ensuring that the predictive model retains critical insights from the bank’s most significant customer segments, leading to more robust and generalizable results.

```{r}
# Finalizing the Behavioral Features
vars_to_cap <- c("monetary", "frequency", "customer_lifetime_value")

modeling_data <- modeling_data %>%
  mutate(across(all_of(vars_to_cap), ~ {
    upper_limit <- quantile(.x, 0.99, na.rm = TRUE)
    ifelse(.x > upper_limit, upper_limit, .x)
  }))

```

### 4.3 Correlation Matrix

::: panel-tabset
## Plot

```{r, echo=FALSE}
# 1. Isolate numeric variables 
numeric_vars <- modeling_data %>% 
  select(where(is.numeric))

# 2. Compute the matrix
cor_matrix <- cor(numeric_vars, use = "pairwise.complete.obs")

# 3. Render with Numbers
corrplot(cor_matrix, 
         method = "color", 
         type = "upper", 
         order = "hclust", 
         addCoef.col = "black", # This adds the correlation numbers
         number.cex = 0.4,      # Crucial: tiny font so 42x42 numbers fit
         tl.col = "black", 
         tl.srt = 45, 
         tl.cex = 0.5, 
         diag = FALSE, 
         title = "\n\nCorrelation Matrix with Coefficients",
         mar = c(0,0,3,0))
```

## Code

```{r, eval=FALSE}
# 1. Isolate numeric variables 
numeric_vars <- modeling_data %>% 
  select(where(is.numeric))

# 2. Compute the matrix
cor_matrix <- cor(numeric_vars, use = "pairwise.complete.obs")

# 3. Render with Numbers
corrplot(cor_matrix, 
         method = "color", 
         type = "upper", 
         order = "hclust", 
         addCoef.col = "black", # This adds the correlation numbers
         number.cex = 0.4,      # Crucial: tiny font so 42x42 numbers fit
         tl.col = "black", 
         tl.srt = 45, 
         tl.cex = 0.5, 
         diag = FALSE, 
         title = "\n\nCorrelation Matrix with Coefficients",
         mar = c(0,0,3,0))
```
:::

The feature set was refined to ensure model integrity and transition from descriptive to predictive analysis. `monetary` and `base_satisfaction` were removed to resolve multicollinearity, as they were highly redundant with `customer_lifetime_value` ($r = 0.96$) and `nps_score` ($r = 0.78$), respectively. Additionally, `risk_group` and `active_products` were excluded to eliminate data leakage. Because `active_products` acted as a lagging mathematical proxy for the target ($r = -0.88$), its removal forced the model to rely on proactive behavioral signals—such as app engagement and sentiment—that allow for genuine early intervention.

```{r}
# Finalizing the features by removing leaky and redundant variables
modeling_data_final <- modeling_data %>%
  select(
    -monetary,        # Removed due to high multicollinearity (r = 0.96) with CLV
    -risk_group,      # Removed to prevent leakage (directly derived from target)
    -active_products,  # Removed as a lagging indicator (r = -0.88 with target)
    -base_satisfaction   # Redundant with nps_score (r = 0.78)
  )
```

```{r}
# List final column names 
colnames(modeling_data_final)
```

### 4.4 Stratified Random Sampling

To evaluate model performance and generalizability, the finalized dataset was partitioned using **stratified random sampling**. An **80/20 split** was implemented, resulting in a training set of approximately 39,000 observations and a holdout testing set of 9,700 observations. Stratification was applied to the `churn_probability` target to ensure that both subsets maintained an identical risk distribution, providing a robust foundation for the subsequent training phase.

```{r}
# Set seed for reproducibility (so you get the same 'random' split every time)
set.seed(123)

# Create the split (80% Training, 20% Testing)
# We stratify by churn_probability to keep the risk distribution consistent
data_split <- initial_split(modeling_data_final, 
                           prop = 0.80, 
                           strata = churn_probability)

# 3. Extract the sets
train_data <- training(data_split)
test_data  <- testing(data_split)

# 4. Verify the split sizes
nrow(train_data) 
nrow(test_data)  
```

### 4.5 Variance Inflation Factor (VIF)

```{r}
my_model <- lm(churn_probability ~ ., data = train_data)

# This will show you the exact variables that are perfectly correlated
alias(my_model)
```

```{r}
# Fits the model without the redundant average column
my_model_fixed <- lm(churn_probability ~ . - product_satisfaction, data = train_data)
# Calculate VIF
vif(my_model_fixed)

```

```{r}
# Remove the variables from the training data
train_data <- train_data %>%
  select(-product_satisfaction, -tx_satisfaction)

# Remove the EXACT SAME variables from the testing data
test_data <- test_data %>%
  select(-product_satisfaction, -tx_satisfaction)
```

::: callout-note
# Remove perfect/high multicollinearity variables

During the multicollinearity assessment on the training set, `product_satisfaction` was identified as having perfect multicollinearity (aliased), as it was an exact linear combination of the five individual banking product indicators. Consequently, it was removed to prevent information redundancy and distortion of feature importance. Subsequently, a Variance Inflation Factor (VIF) analysis was conducted, revealing that `tx_satisfaction` exceeded the conservative threshold of 5.0 (VIF = 5.21). To ensure strict model stability and maintain highly interpretable feature importance rankings for the final tree-based models (Random Forest and XGBoost), `tx_satisfaction` was also eliminated. To maintain feature alignment for model evaluation, these removals were identically applied to the testing dataset.
:::

## 5 Building Predictive Models

For the predictive modeling phase, **Random Forest** and **XGBoost** were selected due to their superior ability to handle the non-linear relationships and complex feature interactions inherent in banking behavioral data. Random Forest provides a robust, ensemble-based baseline that reduces variance by averaging multiple decision trees, making it highly resistant to overfitting. In contrast, XGBoost (Extreme Gradient Boosting) was chosen for its iterative optimization process, which minimizes residual errors and typically yields higher precision in identifying subtle churn signals. Both models are natively capable of handling the mixed data types in this study—ranging from categorical sentiment scores to capped financial metrics—without requiring the strict linearity assumptions of traditional regression models.

### 5.1 Create the Preprocessing Recipe

This recipe will automatically clean the data for both models. Since we have categorical variables like `gender` and `occupation`, we must convert them into a numeric format (Dummy Encoding).

```{r}
# Building the recipe
churn_recipe <- recipe(churn_probability ~ ., data = train_data) %>%
# Force logical/character columns to factors so they can be 'dummified'
  step_mutate_at(all_nominal_predictors(), all_logical_predictors(), fn = as.factor) %>%
  # Create 0/1 numeric columns for all categorical/logical features
  step_dummy(all_nominal_predictors()) %>%
  # Remove variables with zero variance
  step_zv(all_predictors()) %>%
  # Normalize all numbers (optional but good practice)
  step_normalize(all_numeric_predictors())
```

### 5.2 Define and Fit the Models

#### 5.2.1 Define Random Forest

```{r}
# Define Random Forest
rf_spec <- rand_forest(trees = 500) %>%
  set_engine("ranger", importance = "impurity") %>%
  set_mode("regression")

# Fit the model
rf_fit <- workflow() %>%
  add_recipe(churn_recipe) %>%
  add_model(rf_spec) %>%
  fit(data = train_data)

```

#### 5.2.2 Define XGBoost

```{r}
xgb_spec <- boost_tree(trees = 1000, learn_rate = 0.01) %>%
  set_engine("xgboost") %>%
  set_mode("regression")

# Fit the model
xgb_fit <- workflow() %>%
  add_recipe(churn_recipe) %>%
  add_model(xgb_spec) %>%
  fit(data = train_data)

```

#### 5.2.3 Performance Comparison

```{r}
# Compare results
results <- bind_rows(
  predict(rf_fit, test_data) %>% bind_cols(test_data) %>% mutate(model = "Random Forest"),
  predict(xgb_fit, test_data) %>% bind_cols(test_data) %>% mutate(model = "XGBoost")
)

# Calculate RMSE and R-Squared
results %>%
  group_by(model) %>%
  metrics(truth = churn_probability, estimate = .pred)
```

#### 5.2.4 Performance Visualisation

```{r}
# 1. Performance Visualization: Predicted vs. Actual
p_perf <- ggplot(results, aes(x = churn_probability, y = .pred, color = model)) +
  geom_point(alpha = 0.3) +
  geom_abline(lty = 2, color = "black") + # The 'perfect prediction' line
  facet_wrap(~model) +
  theme_minimal() +
  labs(title = "Model Competition: Predicted vs. Actual Churn Probability",
       subtitle = "Proximity to the dashed line indicates higher predictive accuracy",
       x = "Actual Probability", y = "Predicted Probability")

# 2. Variable Importance Visualization
# Random Forest VIP
vip_rf <- rf_fit %>% 
  extract_fit_parsnip() %>% 
  vip(num_features = 10) + 
  labs(title = "Random Forest: Top 10 Drivers")

# XGBoost VIP
vip_xgb <- xgb_fit %>% 
  extract_fit_parsnip() %>% 
  vip(num_features = 10) + 
  labs(title = "XGBoost: Top 10 Drivers")

# Display the performance plot
p_perf

# Combine and display VIP plots side-by-side
vip_rf + vip_xgb
```

## 6 UI Design
