---
title: "Hands-on Exercise 1"
author: "Xu Qianqian"
date: "January 13, 2026"
date-modified: "last-modified"
execute: 
  eval: true
  echo: true
  warning: false
  freeze: true
---

# 1 Overview

A Layered Grammar of Graphics: ggplot2 methods.

# 2 Installing and loading the required libraries

```{r}
pacman::p_load(tidyverse)
```

# 3 Importing data

```{r}
exam_data <- read_csv("data/Exam_data.csv")
```

# 4 R Graphics VS ggplot

```{r}
hist(exam_data$MATHS)

ggplot(data=exam_data, aes(x = MATHS)) +
  geom_histogram(bins=10, 
                 boundary = 100,
                 color="black", 
                 fill="grey") +
  ggtitle("Distribution of Maths scores")
```

# 5 Essential Grammatical Elements in ggplot2

## 5.1 Data

```{r}
ggplot(data=exam_data)
```

## 5.2 Aesthetics

```{r}
ggplot(data=exam_data, 
       aes(x= MATHS))
```

## 5.3 Geometries

### 5.3.1 Geometric Objects: geom_bar

```{r}
ggplot(data=exam_data, 
       aes(x=RACE)) +
  geom_bar()

```

### 5.3.2 Geometric Objects: geom_dotplot

```{r}
ggplot(data=exam_data, 
       aes(x = MATHS)) +
  geom_dotplot(dotsize = 0.5)

```

::: callout-warning
## Be warned

The y scale is not very useful, in fact it is very misleading.
:::

::: callout-note
## Note

The code chunk below performs the following two steps:

-   `scale_y_continuous()` is used to turn off the y-axis, and
-   *binwidth argument* is used to change the binwidth to 2.5.
:::

```{r}
ggplot(data=exam_data, 
       aes(x = MATHS)) +
  geom_dotplot(binwidth=2.5,         
               dotsize = 0.5) +      
  scale_y_continuous(NULL,           
                     breaks = NULL)  
```

### 5.3.3 Geometric Objects: geom_histogram

```{r}
ggplot(data=exam_data, 
       aes(x = MATHS)) +
  geom_histogram()       
```

::: callout-note
## Note

The default bin is **30**.
:::

### 5.3.4 Modifying a gemetric object by changing geom()

In the code chunk below,

-   *bins* argument is used to change the number of bins to 20,

-   *fill* argument is used to shade the histogram with light blue color, and

-   *color* argument is used to change the outline colour of the bars in black

```{r}
ggplot(data=exam_data, 
       aes(x= MATHS)) +
  geom_histogram(bins=20,            
                 color="black",      
                 fill="light blue")  

```

### 5.3.5 Modifying a geometric object by changing aes()

The code chunk below changes the interior colour of the histogram (i.e. *fill*) by using sub-group of *aesthetic()*.

```{r}
ggplot(data=exam_data, 
       aes(x= MATHS, 
           fill = GENDER)) +
  geom_histogram(bins=20, 
                 color="grey30")
```

::: callout-note
## Note

This approach can be used to colour, fill and alpha of the geometric.
:::

### 5.3.6 Geometric Objects: geom-density()

```{r}
ggplot(data=exam_data, 
       aes(x = MATHS)) +
  geom_density()           
```

The code chunk below plots two kernel density lines by using *colour* or *fill* arguments of *aes()*.

```{r}
ggplot(data=exam_data, 
       aes(x = MATHS, 
           colour = GENDER)) +
  geom_density()         
```

### 5.3.7 Geometric Objects: geom_boxplot

```{r}
ggplot(data=exam_data, 
       aes(y = MATHS,       
           x= GENDER)) +    
  geom_boxplot()                   
```

**Notches** are used in box plots to help visually assess whether the medians of distributions differ. If the notches do not overlap, this is evidence that the medians are different.

The code chunk below plots the distribution of Maths scores by gender in notched plot instead of boxplot.

```{r}
ggplot(data=exam_data, 
       aes(y = MATHS, 
           x= GENDER)) +
  geom_boxplot(notch=TRUE)                  
```

### 5.3.8 Geometric Objects: geom_violin

`geom_violin` is designed for creating violin plot. Violin plots are a way of comparing multiple data distributions. With ordinary density curves, it is difficult to compare more than just a few distributions because the lines visually interfere with each other. With a violin plot, it’s easier to compare several distributions since they’re placed side by side.

The code below plot the distribution of Maths score by gender in violin plot.

```{r}
ggplot(data=exam_data, 
       aes(y = MATHS, 
           x= GENDER)) +
  geom_violin()                
```

### 5.3.9 Geometric Objects: geom_point()

`geom_point()` is especially useful for creating scatterplot.

```{r}
ggplot(data=exam_data, 
       aes(x= MATHS, 
           y=ENGLISH)) +
  geom_point()                           
```

### 5.3.10 geom objects can be combined

The code chunk below plots the data points on the boxplots by using both `geom_boxplot()` and `geom_point()`.

```{r}
ggplot(data=exam_data, 
       aes(y = MATHS, 
           x= GENDER)) +
  geom_boxplot() +                    
  geom_point(position="jitter", 
             size = 0.5)                                 
```

## 5.4 Statistics

The [Statistics functions](https://ggplot2.tidyverse.org/reference/index.html#stats) statistically transform data, usually as some form of summary. For example:

-   frequency of values of a variable (bar graph)

    -   a mean

    -   a confidence limit

-   There are two ways to use these functions:

    -   add a `stat_()` function and override the default geom, or

    -   add a `geom_()` function and override the default stat.

### 5.4.1 Working with `stat()`

The boxplots below are incomplete because the positions of the means were not shown.

```{r}
ggplot(data=exam_data, 
       aes(y = MATHS, x= GENDER)) +
  geom_boxplot()

```

### 5.4.2 Working with stat - the `stat_summary()` method

The code chunk below adds mean values by using `stat_summary()` function and overriding the default geom.

```{r}
ggplot(data=exam_data, 
       aes(y = MATHS, x= GENDER)) +
  geom_boxplot() +
  stat_summary(geom = "point",       
               fun = "mean",         
               colour ="red",        
               size=4)               
```

### 5.4.3 Working with stat - the `geom()` method

The code chunk below adding mean values by using `geom_()` function and overriding the default stat.

```{r}
ggplot(data=exam_data, 
       aes(y = MATHS, x= GENDER)) +
  geom_boxplot() +
  geom_point(stat="summary",        
             fun="mean",           
             colour="red",          
             size=4)                       
```

### 5.4.4 Adding a best fit curve on a scatterplot?

The scatterplot below shows the relationship of Maths and English grades of pupils. The interpretability of this graph can be improved by adding a best fit curve.

```{r, echo = FALSE}
ggplot(data=exam_data, 
       aes(x= MATHS, y=ENGLISH)) +
  geom_point()                    
```

In the code chunk below, `geom_smooth()` is used to plot a best fit curve on the scatterplot.

```{r}
ggplot(data=exam_data, 
       aes(x= MATHS, y=ENGLISH)) +
  geom_point() +
  geom_smooth(size=0.5)                    
```

::: callout-note
## Note

The default method used is *loess*.
:::

The default smoothing method can be overridden as shown below.

```{r}
ggplot(data=exam_data, 
       aes(x= MATHS, 
           y=ENGLISH)) +
  geom_point() +
  geom_smooth(method=lm, 
              linewidth=0.5)                  
```

## 5.5 Facets
Facetting generates small multiples (sometimes also called trellis plot), each displaying a different subset of the data. They are an alternative to aesthetics for displaying additional discrete variables. ggplot2 supports two types of factes, namely: `facet_grid()` and `facet_wrap`.






