---
title: "Take-home Exercise 1"
author: "Xu Qianqian"
date: "February 7, 2026"
date-modified: "last-modified"
execute: 
  eval: true
  echo: true
  warning: false
  freeze: true
---

# A Multi-Factorial Analysis of Student Performance in Vietnam’s Higher Education

# 1 Overview

## 1.1 Background

Student outcomes are influenced by a diverse array of factors. Understanding the intricate relationship between student demographics, individual perceptions, and external variables is essential for fostering an effective learning environment. Furthermore, these insights empower lecturers, academic advisors, and educational administrators to implement timely interventions, ultimately enhancing overall student performance.

## 1.2 Our Task

For this take-home exercise, both descriptive and inferential methods are employed to explore survey data. Utilizing visually-driven analysis, this report reveals and communicates key observations. The primary focus is on identifying patterns, trends, and relationships within the responses to interpret results effectively and inform data-driven decision-making.

# 2 Install and load Packages

In this exercise, we will utilize eight R packages to facilitate data import, manipulation, and advanced visualization:

-   **readxl**: For importing data from Excel spreadsheets.

-   **tidyverse**: A collection of fundamental R packages designed for data science, covering everything from data cleaning to creating static statistical graphs.

-   **ggthemes**: Provides additional themes, geometries, and scales to extend the styling capabilities of `ggplot2`.

-   **ggstatsplot**: Enhances `ggplot2` by adding the results of statistical tests directly onto information-rich plots.

-   **patchwork**: An intuitive tool for combining multiple `ggplot2` objects into a single composite figure.

The following code chunk checks for the presence of these packages, installs any that are missing, and loads them into your R environment.

```{r}
pacman::p_load(readxl, tidyverse, ggthemes, ggstatsplot, patchwork)
```

# 3 Data Preparation

## 3.1 The data

For this take-home exercise, we will use the **"Dataset of factors affecting learning outcomes of students at the University of Education, Vietnam National University, Hanoi,"** which was downloaded from \[<https://data.mendeley.com/datasets/23ppcdbmhc/1>\].

This dataset was constructed to facilitate research into student management and the diverse factors influencing academic performance. The data was gathered via a survey conducted from March to June 2023, resulting in **2,170 responses** from students and alumni of the University of Education (VNU-UEd). The data is stored in a file named `Database paper.xlsx` within the `Dataset about VNU studnets` sub-folder of the project directory.

## 3.2 Import Data

The following code chunk utilizes the `read_excel()` function from the **readxl** package to import the dataset into the R environment.

```{r}
survey_data <- read_excel("./Dataset about VNU students/Database paper.xlsx")
```

The `survey_data` tibble consists of **22 variables**, all of which are **categorical**. These can be further classified into nominal and ordinal data types:

-   **Nominal Variables (6):** These variables represent categories with no inherent rank or numerical order. They include:

    -   `Gender`, `Policy_Stu`, `Minority_Stu`, `Poor_Stu`, `Father_Occupation`, and `Mother_Occupation`.

-   **Ordinal Variables (16):** These variables represent categories with a logical sequence or scale (e.g., education levels or Likert scales). They include:

    -   **Demographics & Habits:** `Year`, `Father_Edu`, `Mother_Edu`, `Time_Friends`, `Time_SocicalMedia`, `Time_Studying`, and `GPA`.

    -   **Perceptions & Environment (Likert Scales):** `Adapt_Learning_Uni`, `Study_Methods`, `SupportOf_Uni`, `SupportOf_Lec`, `Facilitie_Uni`, `Quality_Lecturer`, `TrainingCurriculum`, `Competitive_Class`, and `InfluenceF_Friends`.

## 3.3 Preparing the Data

### 3.3.1 Check Missing Values

```{r}
sum(is.na(survey_data))
```

A preliminary data validation check confirmed that the dataset contains no missing values (NAs) across all 22 variables, ensuring a complete sample of 2,170 observations for analysis.

### 3.3.2 Data Wrangling and Factoring

Raw numeric survey responses were recoded into meaningful text labels and converted into factors to ensure logical sequencing for visualization using the code chunk below.

```{r}
survey_data <- survey_data %>%
  mutate(
    # --- NOMINAL VARIABLES ---
    Gender = factor(Gender, levels = c(1, 2), labels = c("Male", "Female")),
    Policy_Stu = factor(Policy_Stu, levels = c(1, 2), labels = c("Yes", "No")),
    Minority_Stu = factor(Minority_Stu, levels = c(1, 2), labels = c("Yes", "No")),
    Poor_Stu = factor(Poor_Stu, levels = c(1, 2), labels = c("Yes", "No")),
    Father_Occupation = factor(Father_Occupation, levels = c(1, 2, 3, 4, 5), 
                               labels = c("Government employee", "Self-employment", "Freelance", "Other", "Not public")),
    Mother_Occupation = factor(Mother_Occupation, levels = c(1, 2, 3, 4, 5), 
                               labels = c("Government employee", "Self-employment", "Freelance", "Other", "Not public")),

    # --- ORDINAL VARIABLES (Demographics & Habits) ---
    Year = factor(Year, levels = c(1, 2, 3, 4, 5), 
                  labels = c("First-year", "Second-year", "Third-year", "Fourth-year", "Graduated"), ordered = TRUE),
    Father_Edu = factor(Father_Edu, levels = c(1, 2, 3, 4, 5, 6), 
                        labels = c("Primary school", "Secondary school", "High school", "College school", "University/graduate education", "Other"), ordered = TRUE),
    Mother_Edu = factor(Mother_Edu, levels = c(1, 2, 3, 4, 5, 6), 
                        labels = c("Primary school", "Secondary school", "High school", "College school", "University/graduate education", "Other"), ordered = TRUE),
    Time_Friends = factor(Time_Friends, levels = c(1, 2, 3, 4, 5), 
                          labels = c("under 1 hour", "from 1 to lower 2 hours", "from 2 to lower 3 hours", "from 3 to lower 4 hours", "over 4 hours"), ordered = TRUE),
    Time_SocicalMedia = factor(Time_SocicalMedia, levels = c(1, 2, 3, 4, 5), 
                               labels = c("under 1 hour", "from 1 to lower 2 hours", "from 2 to lower 3 hours", "from 3 to lower 4 hours", "over 4 hours"), ordered = TRUE),
    Time_Studying = factor(Time_Studying, levels = c(1, 2, 3, 4, 5), 
                           labels = c("under 2 hours", "from 2 to lower 4 hours", "from 4 to lower 6 hours", "from 6 to lower 8 hours", "over 8 hour"), ordered = TRUE),
    GPA = factor(GPA, levels = c(1, 2, 3, 4, 5), 
                 labels = c("Under 2.0 – Poor", "From 2.0 to lower 2.5 – Average", "From 2.5 to lower 3.2 – Fair", "From 3.2 to lower 3.6 – Good", "Over 3.6 – Excellent"), ordered = TRUE)
  ) %>%
  # --- ORDINAL VARIABLES (Likert Scales) ---
  # Using across() to apply the same levels to all 9 environmental factors at once
  mutate(across(c(Adapt_Learning_Uni, Study_Methods, SupportOf_Uni, SupportOf_Lec, Facilitie_Uni, 
                  Quality_Lecturer, TrainingCurriculum, Competitive_Class, InfuenceF_Friends),
                ~ factor(.x, levels = c(1, 2, 3, 4, 5), 
                         labels = c("Not at all", "Little", "Moderate", "Quite", "Very"), ordered = TRUE)))

```

### 3.3.3 Glimpse of Data

```{r}
# Display the first 10 rows of the processed dataset
glimpse(survey_data)
```

# 4 Key Observations

## 4.1 Demographic Profile

### 4.1.1 Academic Year

::: panel-tabset
## Plot

```{r, echo=FALSE}
ggplot(survey_data, aes(x = Year, fill = Year)) +
  geom_bar() +
  stat_count(geom = "text", aes(label = after_stat(count)), 
             vjust = -0.8, size = 3, fontface = "bold") +
  scale_fill_economist() +
  scale_x_discrete(drop=FALSE)+
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Distribution of respondents across academic years", x = NULL, y = NULL) +
  theme_economist() +
  theme(legend.position = "none", 
        axis.text.x = element_text(size = 8),
        axis.ticks.x = element_blank()) + # Removes the x-axis ticks
  coord_cartesian(clip = "off")
```

## Code

```{r, eval=FALSE}
ggplot(survey_data, aes(x = Year, fill = Year)) +
  geom_bar() +
  stat_count(geom = "text", aes(label = after_stat(count)), 
             vjust = -0.8, size = 3, fontface = "bold") +
  scale_fill_economist() +
  scale_x_discrete(drop=FALSE)+
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Distribution of respondents across academic years", x = NULL, y = NULL) +
  theme_economist() +
  theme(legend.position = "none", 
        axis.text.x = element_text(size = 8),
        axis.ticks.x = element_blank()) + # Removes the x-axis ticks
  coord_cartesian(clip = "off")
```
:::

::: callout-note
## Things we can learn from the plot

-   The **Academic Year** plot reveals a significant skew in the respondent base:
    -   **Sample Concentration:** The vast majority of respondents are either **Graduated (1,594)** or **Fourth-year (441)** students.

    -   **Missing Data:** There is zero representation from First-year and Second-year students.

    -   This means that the findings on GPA and institutional perceptions reflect only those who have completed most or all of their academic journey.
:::

### 4.1.2 Gender

::: panel-tabset
## Plot

```{r, echo=FALSE, fig.width=8, fig.height=8}
ggbarstats(
  data = survey_data,
  x = GPA,           
  y = Gender,          
  title = "Academic Performance By Gender",
  package = "ggsci",    
  palette = "nrc_npg",
  ggtheme = theme_economist() 
) + 
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(t = 20), 
    legend.text = element_text(size = 8),
    plot.title = element_text(margin = margin(b = 20)) 
  )

```

## Code

```{r, eval=FALSE, fig.width=8, fig.height=8}
ggbarstats(
  data = survey_data,
  x = GPA,           
  y = Gender,          
  title = "Academic Performance By Gender",
  package = "ggsci",    
  palette = "nrc_npg",
  ggtheme = theme_economist() 
) + 
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(t = 20), 
    legend.text = element_text(size = 8),
    plot.title = element_text(margin = margin(b = 20)) 
  )

```
:::

::: callout-note
## Things we can learn from the plot

-   The dataset is heavily skewed toward female respondents, who make up approximately **89%** of the total sample ($n=2,170$)

-   The analysis confirms a statistically significant gender gap in academic achievement ($p = 0.03$). While over half of all students maintain a 'Fair' GPA, female respondents are significantly more likely to reach 'Excellent' standing ($>3.6$) and less likely to fall into the 'Poor' or 'Average' categories compared to their male counterparts.
:::

### 4.1.3 Ethnic Status

::: panel-tabset
## Plot

```{r, echo=FALSE, fig.width=8, fig.height=8}
# 1. Re-label the existing factor levels for the plot
survey_data %>%
  mutate(Minority_Stu = factor(Minority_Stu, 
                               levels = c("Yes", "No"),
                               labels = c("Minority Students", "Non-Minority Students"))) %>%
# 2. Execute the plot
ggbarstats(
  x = GPA,           
  y = Minority_Stu,          
  title = "Academic Performance By Ethnic Status",
  legend.title = "GPA Bracket",
  package = "ggsci",    
  palette = "nrc_npg",
  ggtheme = theme_economist() 
) + 
  # 3. Apply the legend and layout fixes
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(t = 20), 
    legend.text = element_text(size = 8),
    plot.title = element_text(margin = margin(b = 20)),
    axis.title.x = element_blank() 
  )

```

## Code

```{r, eval=FALSE, fig.width=8, fig.height=8}
# 1. Re-label the existing factor levels for the plot
survey_data %>%
  mutate(Minority_Stu = factor(Minority_Stu, 
                               levels = c("Yes", "No"),
                               labels = c("Minority Student", "Non-Minority Student"))) %>%
# 2. Execute the plot
ggbarstats(
  x = GPA,           
  y = Minority_Stu,          
  title = "Academic Performance By Ethnic Status",
  legend.title = "GPA Bracket",
  package = "ggsci",    
  palette = "nrc_npg",
  ggtheme = theme_economist() 
) + 
  # 3. Apply the legend and layout fixes
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(t = 20), 
    legend.text = element_text(size = 8),
    plot.title = element_text(margin = margin(b = 20)),
    axis.title.x = element_blank() 
  )

```
:::

::: callout-note
## Things we can learn from the plot

The relationship between ethnic status and academic performance is highly significant ($p < 0.001$), revealing distinct concentration differences between the two groups.

-   **Minority Students:** This group shows a heavy concentration in the "Fair" bracket (**76%**), with minimal representation (**2%**) in the "Excellent" category.

-   **Non-Minority Students:** Performance is more widely distributed, with **33%** achieving a "Good" GPA and **5%** reaching the "Excellent" tier.

-   **Note on Sample Size:** It is important to note the disparity in group sizes; the Minority Student cohort ($n=129$) is significantly smaller than the Non-Minority cohort ($n=2,041$), which may affect the comparative stability of these proportions.
:::

## 4.2 Economic Status

::: panel-tabset
## Plot

```{r, echo=FALSE, fig.width=8, fig.height=8}
# 1. Re-label the existing factor levels for the plot
survey_data %>%
  mutate(Poor_Stu = factor(Poor_Stu, 
                               levels = c("Yes", "No"), 
                               labels = c("From poor household", "Not from poor household"))) %>%
# 2. Execute the plot
ggbarstats(
  x = GPA,           
  y = Poor_Stu,          
  title = "Academic Performance By Household Status",
  legend.title = "GPA Bracket",
  package = "ggsci",    
  palette = "nrc_npg",
  ggtheme = theme_economist() 
) + 
  # 3. Apply the legend and layout fixes
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(t = 20), 
    legend.text = element_text(size = 8),
    plot.title = element_text(margin = margin(b = 20)),
    axis.title.x = element_blank() 
  )

```

## Code

```{r, eval=FALSE, fig.width=8, fig.height=8}
# 1. Re-label the existing factor levels for the plot
survey_data %>%
  mutate(Poor_Stu = factor(Poor_Stu, 
                               levels = c("Yes", "No"), 
                               labels = c("From poor household", "Not from poor household"))) %>%
# 2. Execute the plot
ggbarstats(
  x = GPA,           
  y = Poor_Stu,          
  title = "Academic Performance By Household Status",
  legend.title = "GPA Bracket",
  package = "ggsci",    
  palette = "nrc_npg",
  ggtheme = theme_economist() 
) + 
  # 3. Apply the legend and layout fixes
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(t = 20), 
    legend.text = element_text(size = 8),
    plot.title = element_text(margin = margin(b = 20)),
    axis.title.x = element_blank() 
  )

```
:::

::: callout-note
## Things we can learn from the plot

-   **Marginal Significance**: Unlike gender or ethnicity, the relationship here is not statistically significant at the standard 95% confidence level ($p = 0.07$). This suggests that in this specific sample, economic status is a weaker predictor of GPA than other demographic factors.

-   **Extreme Data Skew**: There is a very large imbalance in sample sizes; only **86 students** identify as being from a poor household, compared to **2,084** who do not.
:::

::: panel-tabset
## Plot

```{r, echo=FALSE}
# Plotting the overlap between Household Status and Policy Support
ggplot(survey_data, aes(x = Poor_Stu, fill = Policy_Stu)) +
  geom_bar(position = "fill") + 
  scale_y_continuous(labels = scales::percent) +
  # Update labels directly in the scale
  scale_fill_economist(labels = c("Receiving Support", "No Support")) + 
  labs(title = "Policy Support Distribution by Household Status",
       x = "Coming from Poor Household",
       y = "Proportion",
       fill = NULL) + # Removes the legend title
  theme_economist() +
  theme(
    axis.ticks.x = element_blank(),
    legend.position = "top",
    legend.justification = "right",
    legend.text = element_text(size = 9)
  )

```

## Code

```{r, eval=FALSE}
# Plotting the overlap between Household Status and Policy Support
ggplot(survey_data, aes(x = Poor_Stu, fill = Policy_Stu)) +
  geom_bar(position = "fill") + 
  scale_y_continuous(labels = scales::percent) +
  # Update labels directly in the scale
  scale_fill_economist(labels = c("Receiving Support", "No Support")) + 
  labs(title = "Policy Support Distribution by Household Status",
       x = "Coming from Poor Household",
       y = "Proportion",
       fill = NULL) + # Removes the legend title
  theme_economist() +
  theme(
    axis.ticks.x = element_blank(),
    legend.position = "top",
    legend.justification = "right",
    legend.text = element_text(size = 9)
  )

```
:::

::: callout-note
## Things we can learn from the plot

-   The analysis reveals a perfect alignment between economic need and government intervention: **100%** of students from poor households are currently receiving government policy support. This universal coverage likely plays a critical role in neutralizing the negative impact of socioeconomic barriers on academic performance, contributing to the non-significant relationship between economic status and GPA ($p = 0.07$).
-   Furthermore, the fact that a significant segment of the non-poor population also receives aid suggests that government eligibility is multi-faceted, likely incorporating merit-based or moderate-need criteria.
:::

## 4.3 Parental Professional Synergy

This section analyzes the combined influence of parental occupations on student achievement, defined here as the combined percentage of "Good" and "Excellent" GPA tiers (GPA \> 3.2). By mapping these career intersections, we identify the Socio-Professional Capital that serves as a foundational driver for academic success.

::: panel-tabset
## Plot

```{r, echo=FALSE, fig.width=8, fig.height=6}
# 1. Prepare and Clean Data
synergy_data <- survey_data %>%
  group_by(Father_Occupation, Mother_Occupation) %>%
  summarise(
    n_students = n(),
    high_perf_count = sum(GPA %in% c("Over 3.6 – Excellent", "From 3.2 to lower 3.6 – Good"), na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    success_rate = (high_perf_count / n_students) * 100,
    Mother_Occupation = stringr::str_wrap(Mother_Occupation, width = 12),
    Father_Occupation = stringr::str_wrap(Father_Occupation, width = 12),
    text_color = ifelse(success_rate > 55, "white", "#333333")
  ) 

# 2. Polished Heatmap
ggplot(synergy_data, aes(x = Mother_Occupation, y = Father_Occupation, fill = success_rate)) +
  geom_tile(color = "white", linewidth = 1.2) + 
  scale_fill_gradient(
    low = "#d9edff", 
    high = "#00407d", 
    name = "SUCCESS RATE (%)",
    guide = guide_colorbar(barwidth = 1, barheight = 10, ticks = FALSE)
  ) +
  geom_text(
    aes(label = paste0(round(success_rate, 0), "%"), color = text_color),
    size = 4,
    fontface = "bold"
  ) +
  scale_color_identity() +
  theme_economist() +
  labs(
    title = "Parental Professional Synergy",
    subtitle = "Combined Success Rate (Good & Excellent GPA) by Career Intersection",
    x = "Mother's Occupation",
    y = "Father's Occupation"
  ) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 0, size = 9, vjust = 0.5),
    axis.text.y = element_text(size = 9),
    axis.title = element_text(size = 10, face = "bold", margin = margin(t = 15)),
    legend.position = "right",
    plot.title = element_text(margin = margin(b = 20), face = "bold", size = 16),
    plot.subtitle = element_text(size = 11, face = "italic")
  )
```

## Code

```{r, eval=FALSE, fig.width=8, fig.height=6}
# 1. Prepare and Clean Data
synergy_data <- survey_data %>%
  group_by(Father_Occupation, Mother_Occupation) %>%
  summarise(
    n_students = n(),
    high_perf_count = sum(GPA %in% c("Over 3.6 – Excellent", "From 3.2 to lower 3.6 – Good"), na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    success_rate = (high_perf_count / n_students) * 100,
    Mother_Occupation = stringr::str_wrap(Mother_Occupation, width = 12),
    Father_Occupation = stringr::str_wrap(Father_Occupation, width = 12),
    text_color = ifelse(success_rate > 55, "white", "#333333")
  ) 

# 2. Polished Heatmap
ggplot(synergy_data, aes(x = Mother_Occupation, y = Father_Occupation, fill = success_rate)) +
  geom_tile(color = "white", linewidth = 1.2) + 
  scale_fill_gradient(
    low = "#d9edff", 
    high = "#00407d", 
    name = "SUCCESS RATE (%)",
    guide = guide_colorbar(barwidth = 1, barheight = 10, ticks = FALSE)
  ) +
  geom_text(
    aes(label = paste0(round(success_rate, 0), "%"), color = text_color),
    size = 4,
    fontface = "bold"
  ) +
  scale_color_identity() +
  theme_economist() +
  labs(
    title = "Parental Professional Synergy",
    subtitle = "Combined Success Rate (Good & Excellent GPA) by Career Intersection",
    x = "Mother's Occupation",
    y = "Father's Occupation"
  ) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 0, size = 9, vjust = 0.5),
    axis.text.y = element_text(size = 9),
    axis.title = element_text(size = 10, face = "bold", margin = margin(t = 15)),
    legend.position = "right",
    plot.title = element_text(margin = margin(b = 20), face = "bold", size = 16),
    plot.subtitle = element_text(size = 11, face = "italic")
  )
```
:::

::: callout-note
## Things we can learn from the plot

-   The highest success rates are found in households where the father’s occupation is categorized as **"Not public"**. Specifically, intersections with mothers in **Self-employment (75%)** and **Government employment (67%)** show the highest density of top-tier academic performers.

-   The lowest success rates (**0% to 10%**) are consistently associated with households where the mother's occupation is **"Not public"**, regardless of the father’s professional background.
:::

## 4.4 Intrinsic Drivers

### 4.4.1 Parental Educational Background

In this section, we analyze how parental educational background relates to students' academic performance. To facilitate a more direct comparison, parental education was consolidated into two distinct categories: **'Basic Education'** and **'Higher Education'**. Due to the ambiguous nature of the **'Other'** category, those responses were excluded from this specific analysis to ensure the integrity of the comparison between formal educational tiers.

```{r}
survey_data_filtered <- survey_data %>%
  mutate(
    Father_Edu_Simple = fct_collapse(Father_Edu,
      "Basic education" = c("Primary school", "Secondary school", "High school"),
      "Higher education" = c("College school", "University/graduate education")
    ),
    Mother_Edu_Simple = fct_collapse(Mother_Edu,
      "Basic education" = c("Primary school", "Secondary school", "High school"),
      "Higher education" = c("College school", "University/graduate education")
    )
  ) %>%
  # Remove "Other" so it doesn't skew the Basic vs. Higher comparison
  filter(Father_Edu_Simple != "Other" & Mother_Edu_Simple != "Other")

```

::: panel-tabset
## Plot

```{r, echo=FALSE}
# 1. Plot for Father's Education
p1 <- ggbarstats(
  data = survey_data_filtered,
  x = GPA,                    
  y = Father_Edu_Simple,      
  label = "percentage",       
  label.args = list(size = 2.5, fill = "white", alpha = 0.7),
  title = "By Father's Education",
  messages = FALSE,
  bf.message = FALSE
) +
  theme_economist() +
  labs(x = NULL)

# 2. Plot for Mother's Education
p2 <- ggbarstats(
  data = survey_data_filtered,
  x = GPA,                    
  y = Mother_Edu_Simple,      
  label = "percentage",       
  label.args = list(size = 2.5, fill = "white", alpha = 0.7),
  title = "By Mother's Education",
  messages = FALSE,
  bf.message = FALSE
) +
  theme_economist() +
  labs(x = NULL)

# 3. Combine with Patchwork
(p1 | p2) + 
  plot_layout(guides = "collect") +
  plot_annotation(
    title = "Impact of Parental Education on Student GPA",
    theme = theme_economist()
  ) & 
  theme(
    # Reduce legend text size to save horizontal space
    legend.text = element_text(size = 7), 
    legend.title = element_text(size = 8, face = "bold"),
    legend.position = "right",
    
    # Increase space between panels but reduce outer margins to expand plots
    panel.spacing = unit(2, "lines"),
    plot.margin = margin(5, 5, 5, 5),
    
    # Clean up axis labels to prevent overlap
    axis.text.x = element_text(size = 7, vjust = 0.5),
    plot.title = element_text(size = 13, face = "bold")
  )
```

## Code

```{r, eval=FALSE}

# 1. Plot for Father's Education
p1 <- ggbarstats(
  data = survey_data_filtered,
  x = GPA,                    
  y = Father_Edu_Simple,      
  label = "percentage",       
  label.args = list(size = 2.5, fill = "white", alpha = 0.7),
  title = "By Father's Education",
  messages = FALSE,
  bf.message = FALSE
) +
  theme_economist() +
  labs(x = NULL)

# 2. Plot for Mother's Education
p2 <- ggbarstats(
  data = survey_data_filtered,
  x = GPA,                    
  y = Mother_Edu_Simple,      
  label = "percentage",       
  label.args = list(size = 2.5, fill = "white", alpha = 0.7),
  title = "By Mother's Education",
  messages = FALSE,
  bf.message = FALSE
) +
  theme_economist() +
  labs(x = NULL)

# 3. Combine with Patchwork
(p1 | p2) + 
  plot_layout(guides = "collect") +
  plot_annotation(
    title = "Impact of Parental Education on Student GPA",
    theme = theme_economist()
  ) & 
  theme(
    # Reduce legend text size to save horizontal space
    legend.text = element_text(size = 7), 
    legend.title = element_text(size = 8, face = "bold"),
    legend.position = "right",
    
    # Increase space between panels but reduce outer margins to expand plots
    panel.spacing = unit(2, "lines"),
    plot.margin = margin(5, 5, 5, 5),
    
    # Clean up axis labels to prevent overlap
    axis.text.x = element_text(size = 7, vjust = 0.5),
    plot.title = element_text(size = 13, face = "bold")
  )
```
:::

::: callout-note
## Things we can learn from the plots

The comparative analysis of parental education reveals a statistically significant relationship with student academic performance.

-   **Positive Performance Shift:** Students with parents from **'Higher Education'** backgrounds demonstrate a clear upward shift in GPA categories compared to the **'Basic Education'** group. Specifically, the proportion of students achieving a **'Good'** GPA increases from **25% to 38%** for Father's education and from **25% to 37%** for Mother's education.

-   **Consistency Across Parents:** The impact is remarkably consistent between both parents. In both cases, the dominant GPA category shifts from **'Fair' (62%)** in the Basic group to a more balanced distribution between **'Fair' (49%)** and **'Good' (\~37%)** in the Higher Education group.

-   **Statistical Significance:** The extremely low $p$-values ($p < .001$) across all groups confirm that these distributions are not random and that parental educational attainment is a robust indicator of a student's academic trajectory.
:::

### 4.4.2 Behavioral Habits & Time Usage

In this section, we evaluate how time spent on studying, social media, and interacting with friends affects student performance. By calculating the success rate—defined as the percentage of students achieving a GPA of 3.2 or higher—across various time intervals, we aim to identify the ideal time commitment for each activity.

::: panel-tabset
## Plot

```{r, echo=FALSE}

# 1. Define High GPA levels based on your factor labels 
high_gpa_levels <- c("From 3.2 to lower 3.6 – Good", "Over 3.6 – Excellent")

# 2. Function to calculate percentage of students achieving a high GPA for each activity
calc_pct <- function(df, var_name) {
  orig_levels <- levels(df[[var_name]])
  
  df %>%
    group_by(Time_Level = !!sym(var_name)) %>%
    summarise(
      pct = (sum(GPA %in% high_gpa_levels) / n()) * 100,
      .groups = "drop"
    ) %>%
    mutate(
      Activity = var_name,
      Time_Level = as.character(Time_Level) 
    )
}

# 3. Combine variables manually 
plot_data <- bind_rows(
  calc_pct(survey_data, "Time_Friends"),
  calc_pct(survey_data, "Time_SocicalMedia"),
  calc_pct(survey_data, "Time_Studying")
)

# 4. Smart Re-factoring: Automatically pulls levels from survey_data 
all_levels <- c(levels(survey_data$Time_Friends), 
                levels(survey_data$Time_SocicalMedia), 
                levels(survey_data$Time_Studying))

plot_data$Time_Level <- factor(plot_data$Time_Level, levels = unique(all_levels))

# 5. Clean Activity labels for display
plot_data <- plot_data %>%
  mutate(Activity = case_when(
    Activity == "Time_Friends" ~ "Time with Friends",
    Activity == "Time_SocicalMedia" ~ "Time on Social Media",
    Activity == "Time_Studying" ~ "Time on Studying"
  ))

# 6. Create the Plot
ggplot(plot_data, aes(x = Time_Level, y = pct, group = Activity, color = Activity)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 3.5) +
  geom_text(aes(label = paste0(round(pct, 1), "%")), 
            vjust = -1.5, size = 3, fontface = "bold", show.legend = FALSE) +
  facet_wrap(~Activity, scales = "free_x", nrow = 1) + 
  scale_y_continuous(limits = c(min(plot_data$pct)-5, max(plot_data$pct)+5)) +
  scale_color_economist() + 
  theme_economist() + 
  labs(title = "Time Allocation Patterns and Academic Success Rates",
       x = NULL, y = "Success Rate (%)") +
theme(
    plot.title = element_text(
      face = "bold", 
      size = 14, 
      margin = margin(b = 30) 
    ),
    panel.spacing = unit(2, "lines"),
    plot.margin = margin(t = 20, r = 15, b = 50, l = 15),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8, color = "black"),
    strip.text = element_text(face = "bold", size = 11, margin = margin(b = 15)),
    legend.position = "none"
  )
```

## Code

```{r, eval=FALSE}

# 1. Define High GPA levels based on your factor labels 
high_gpa_levels <- c("From 3.2 to lower 3.6 – Good", "Over 3.6 – Excellent")

# 2. Function to calculate percentage of students achieving a high GPA for each activity
calc_pct <- function(df, var_name) {
  orig_levels <- levels(df[[var_name]])
  
  df %>%
    group_by(Time_Level = !!sym(var_name)) %>%
    summarise(
      pct = (sum(GPA %in% high_gpa_levels) / n()) * 100,
      .groups = "drop"
    ) %>%
    mutate(
      Activity = var_name,
      Time_Level = as.character(Time_Level) 
    )
}

# 3. Combine variables manually 
plot_data <- bind_rows(
  calc_pct(survey_data, "Time_Friends"),
  calc_pct(survey_data, "Time_SocicalMedia"),
  calc_pct(survey_data, "Time_Studying")
)

# 4. Smart Re-factoring: Automatically pulls levels from survey_data 
all_levels <- c(levels(survey_data$Time_Friends), 
                levels(survey_data$Time_SocicalMedia), 
                levels(survey_data$Time_Studying))

plot_data$Time_Level <- factor(plot_data$Time_Level, levels = unique(all_levels))

# 5. Clean Activity labels for display
plot_data <- plot_data %>%
  mutate(Activity = case_when(
    Activity == "Time_Friends" ~ "Time with Friends",
    Activity == "Time_SocicalMedia" ~ "Time on Social Media",
    Activity == "Time_Studying" ~ "Time on Studying"
  ))

# 6. Create the Plot
ggplot(plot_data, aes(x = Time_Level, y = pct, group = Activity, color = Activity)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 3.5) +
  geom_text(aes(label = paste0(round(pct, 1), "%")), 
            vjust = -1.5, size = 3, fontface = "bold", show.legend = FALSE) +
  facet_wrap(~Activity, scales = "free_x", nrow = 1) + 
  scale_y_continuous(limits = c(min(plot_data$pct)-5, max(plot_data$pct)+5)) +
  scale_color_economist() + 
  theme_economist() + 
  labs(title = "Time Allocation Patterns and Academic Success Rates",
       x = NULL, y = "Success Rate (%)") +
theme(
    plot.title = element_text(
      face = "bold", 
      size = 14, 
      margin = margin(b = 30) 
    ),
    panel.spacing = unit(2, "lines"),
    plot.margin = margin(t = 20, r = 15, b = 50, l = 15),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8, color = "black"),
    strip.text = element_text(face = "bold", size = 11, margin = margin(b = 15)),
    legend.position = "none"
  )
```
:::

::: callout-note
## Things we can learn from the plots

-   **Social Media:** Performance is stable (38–39%) up to 4 hours of use but drops sharply to **27.4%** beyond that threshold, indicating a clear limit for productivity.

-   **Studying:** Success rates peak at **37.6%** for students studying over 8 hours daily. A significant dip to **23.4%** occurs at the 2–4 hour mark, suggesting moderate effort may be insufficient.

-   **Socializing:** A "sweet spot" exists at **1–2 hours** daily (**38.5%** success). Effectiveness declines as social time exceeds 3 hours, likely due to time displacement.

To maximize success, the data suggests prioritizing **6+ hours of study**, limiting social media to **under 4 hours**, and maintaining a balanced **1–2 hours of social interaction**.
:::

## 4.5 Institutional & Environmental Factors

This section evaluates the institutional environment and its perceived influence on learning. By analyzing student assessments of teaching methods, faculty accessibility, and infrastructure, we identify the primary environmental drivers of the academic experience.

### 4.5.1 The Academic & Institutional Ecosystem

A 100% stacked bar chart illustrates student perceptions across various environmental factors and their perceived influence on learning outcomes. By arranging the factors in descending order of 'Very' ratings, the chart highlights the elements students identify as having the most significant impact on their academic experience.

::: panel-tabset
## Plot

```{r, echo=FALSE}
# 1. Prepare Data
likert_long <- survey_data %>%
  select(
    "Adaptation to University" = Adapt_Learning_Uni,
    "Study Methods"             = Study_Methods,
    "University Support"        = SupportOf_Uni,
    "Lecturer Support"          = SupportOf_Lec,
    "University Facilities"     = Facilitie_Uni,
    "Lecturer Quality"          = Quality_Lecturer,
    "University Curriculum"     = TrainingCurriculum,
    "Class Competitiveness"     = Competitive_Class,
    "Peer Influence"            = InfuenceF_Friends
  ) %>%
  pivot_longer(cols = everything(),
               names_to = "Variable",
               values_to = "Response")

# 2. Rank based on 'Very'
rank_order <- likert_long %>%
  group_by(Variable) %>%
  summarize(p_very = sum(Response == "Very") / n()) %>%
  arrange(p_very) %>% 
  pull(Variable)

# 3. Reorder the Factor and Ensure Response Levels are Logical
likert_long <- likert_long %>%
  mutate(Variable = factor(Variable, levels = rank_order),
         Response = factor(Response, levels = c("Not at all", "Little", "Moderate", "Quite", "Very")))

# 4. Final Professional Execution
ggplot(likert_long, aes(x = Variable, fill = Response)) +
  geom_bar(position = "fill", width = 0.6) +
  coord_flip() +
  scale_y_continuous(
    labels = scales::percent_format(), 
    expand = expansion(mult = c(0, 0.02)) 
  ) +
  scale_fill_brewer(palette = "RdYlGn", direction = 1) + 
  
  labs(
    title = "Perceptions of the Institutional Environment",
    x = NULL,        
    y = "Percentage of Responses",
    fill = "Rating:"
  ) +
  theme_economist() + 
  theme(
    plot.title = element_text(face = "bold", size = 15, margin = margin(b = 40), hjust = 0),
    axis.text.y = element_text(size = 9, face = "bold", color = "black"),
    axis.text.x = element_text(size = 9),
    axis.title.x = element_text(size = 10, margin = margin(t = 15), face = "italic"),
    
    legend.position = "top", 
    legend.justification = "left",
    legend.direction = "horizontal",
    legend.title = element_text(size = 9, face = "bold"),
    legend.text = element_text(size = 8),
    plot.margin = margin(t = 30, r = 40, b = 25, l = 15),
    
    # Cleaning up the grid
    panel.grid.major.y = element_blank(), 
    axis.line.x = element_line(size = 0.5, color = "black")
  ) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE, reverse = FALSE))
```

## Code

```{r, eval=FALSE}
# 1. Prepare Data
likert_long <- survey_data %>%
  select(
    "Adaptation to University" = Adapt_Learning_Uni,
    "Study Methods"             = Study_Methods,
    "University Support"        = SupportOf_Uni,
    "Lecturer Support"          = SupportOf_Lec,
    "University Facilities"     = Facilitie_Uni,
    "Lecturer Quality"          = Quality_Lecturer,
    "University Curriculum"     = TrainingCurriculum,
    "Class Competitiveness"     = Competitive_Class,
    "Peer Influence"            = InfuenceF_Friends
  ) %>%
  pivot_longer(cols = everything(),
               names_to = "Variable",
               values_to = "Response")

# 2. Rank based on 'Very'
rank_order <- likert_long %>%
  group_by(Variable) %>%
  summarize(p_very = sum(Response == "Very") / n()) %>%
  arrange(p_very) %>% 
  pull(Variable)

# 3. Reorder the Factor and Ensure Response Levels are Logical
likert_long <- likert_long %>%
  mutate(Variable = factor(Variable, levels = rank_order),
         Response = factor(Response, levels = c("Not at all", "Little", "Moderate", "Quite", "Very")))

# 4. Final Professional Execution
ggplot(likert_long, aes(x = Variable, fill = Response)) +
  geom_bar(position = "fill", width = 0.6) +
  coord_flip() +
  scale_y_continuous(
    labels = scales::percent_format(), 
    expand = expansion(mult = c(0, 0.02)) 
  ) +
  scale_fill_brewer(palette = "RdYlGn", direction = 1) + 
  
  labs(
    title = "Perceptions of the Institutional Environment",
    x = NULL,        
    y = "Percentage of Responses",
    fill = "Rating:"
  ) +
  theme_economist() + 
  theme(
    plot.title = element_text(face = "bold", size = 15, margin = margin(b = 40), hjust = 0),
    axis.text.y = element_text(size = 9, face = "bold", color = "black"),
    axis.text.x = element_text(size = 9),
    axis.title.x = element_text(size = 10, margin = margin(t = 15), face = "italic"),
    
    legend.position = "top", 
    legend.justification = "left",
    legend.direction = "horizontal",
    legend.title = element_text(size = 9, face = "bold"),
    legend.text = element_text(size = 8),
    plot.margin = margin(t = 30, r = 40, b = 25, l = 15),
    
    # Cleaning up the grid
    panel.grid.major.y = element_blank(), 
    axis.line.x = element_line(size = 0.5, color = "black")
  ) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE, reverse = FALSE))
```
:::

::: callout-note
## Things we can learn from the plots

A granular analysis of the environment reveals that **Lecturer Quality** is the sole institutional factor to exceed the 50% threshold for 'Very' responses. This positions instructional excellence as the singular dominant strength of the academic ecosystem, while all other factors—including lecturer support, facilities, and curriculum—are perceived as secondary drivers of the student experience.
:::

### 4.5.2 Systemic Interdependencies

This section examines the underlying relationships between student perceptions and academic achievement, utilizing Spearman’s Rank Correlation to identify which environmental drivers are most strongly linked to GPA outcomes.

::: panel-tabset
## Plot

```{r,echo=FALSE, fig.width=10, fig.height=8}
# We convert factors to numeric levels (1-5) to calculate Spearman's rho
cor_data <- survey_data %>%
  select(
    "GPA" = GPA,
    "Adaptation to University" = Adapt_Learning_Uni,
    "Study Methods"             = Study_Methods,
    "University Support"        = SupportOf_Uni,
    "Lecturer Support"          = SupportOf_Lec,
    "University Facilities"     = Facilitie_Uni,
    "Lecturer Quality"          = Quality_Lecturer,
    "University Curriculum"     = TrainingCurriculum,
    "Class Competitiveness"     = Competitive_Class,
    "Peer Influence"            = InfuenceF_Friends
  ) %>%
  # Ensure they are ordered factors first, then convert to numeric
  mutate(across(everything(), ~as.numeric(factor(.x, ordered = TRUE))))


# 2. Generate the plot 
ggcorrmat(
  data = cor_data,
  type = "nonparametric",    # Spearman correlation
  matrix.type = "lower",    
  lab = TRUE,                
  lab_size = 3.5,            # Slightly smaller to fit inside boxes
  digits = 2,                
  sig.level = 0.05,
  p.adjust.method = "holm",
  colors = c("#d7191c", "#ffffbf", "#1a9641"), 
  title = "Systemic Interdependencies: Perception & Achievement",
  subtitle = "Spearman's Rank Correlation Matrix",
  hc.order = TRUE,           # Groups variables by similarity
  ggtheme = theme_economist()
) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10, color = "black"),
    axis.text.y = element_text(size = 10, color = "black"),
    plot.title = element_text(face = "bold", size = 15, hjust = 0),
    plot.subtitle = element_text(size = 11, face = "italic", margin = margin(b = 20), hjust = 0),
    plot.margin = margin(t = 20, r = 20, b = 20, l = 20),
    legend.position = "right",
    panel.grid.major = element_blank() 
  )
  
```

## Code

```{r,eval=FALSE, fig.width=10, fig.height=8}
# We convert factors to numeric levels (1-5) to calculate Spearman's rho
cor_data <- survey_data %>%
  select(
    "GPA" = GPA,
    "Adaptation to University" = Adapt_Learning_Uni,
    "Study Methods"             = Study_Methods,
    "University Support"        = SupportOf_Uni,
    "Lecturer Support"          = SupportOf_Lec,
    "University Facilities"     = Facilitie_Uni,
    "Lecturer Quality"          = Quality_Lecturer,
    "University Curriculum"     = TrainingCurriculum,
    "Class Competitiveness"     = Competitive_Class,
    "Peer Influence"            = InfuenceF_Friends
  ) %>%
  # Ensure they are ordered factors first, then convert to numeric
  mutate(across(everything(), ~as.numeric(factor(.x, ordered = TRUE))))


# 2. Generate the plot 
ggcorrmat(
  data = cor_data,
  type = "nonparametric",    # Spearman correlation
  matrix.type = "lower",    
  lab = TRUE,                
  lab_size = 3.5,            # Slightly smaller to fit inside boxes
  digits = 2,                
  sig.level = 0.05,
  p.adjust.method = "holm",
  colors = c("#d7191c", "#ffffbf", "#1a9641"), 
  title = "Systemic Interdependencies: Perception & Achievement",
  subtitle = "Spearman's Rank Correlation Matrix",
  hc.order = TRUE,           # Groups variables by similarity
  ggtheme = theme_economist()
) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10, color = "black"),
    axis.text.y = element_text(size = 10, color = "black"),
    plot.title = element_text(face = "bold", size = 15, hjust = 0),
    plot.subtitle = element_text(size = 11, face = "italic", margin = margin(b = 20), hjust = 0),
    plot.margin = margin(t = 20, r = 20, b = 20, l = 20),
    legend.position = "right",
    panel.grid.major = element_blank() 
  )
  
```
:::

::: callout-note
## Things we can learn from the plots

-   **Decoupling of Perception and Performance:** Although **Lecturer Quality** exceeded the 50% "Very" satisfaction threshold, the correlation between environmental factors and GPA remains notably low or statistically non-significant.

-   **Statistical Non-Significance:** Key variables—including **University Support**, **Facilities**, **Class Competitiveness**, and **Peer Influence**—show no significant relationship with GPA ($p > 0.05$), as indicated by the "X" markings.

-   **Institutional Role as a "Setting":** These results suggest that while the environment provides a high-quality academic setting, it does not function as a direct determinant of grades.
:::

# 5 Conclusion

The analysis provides a comprehensive look at the drivers of academic success and institutional perception within the university. While the university excels in the quality of its teaching staff, student performance is influenced by a complex interplay of personal behavior and demographic factors.

### **Limitations of the Dataset**

Despite the depth of the findings, several critical limitations must be acknowledged regarding the sample composition:

-   **Academic Year Skew:** The data exclusively reflects "senior" perspectives, as the sample is heavily weighted toward Graduated and Fourth-year students, with zero representation from junior cohorts.

-   **Gender Imbalance:** The respondent base is predominantly female compared to a much smaller male group, which may limit the generalizability of the male performance profile.

-   **Ethnic Majority Dominance:** The sample is significantly skewed toward the ethnic majority versus a smaller minority cohort, making the findings for the latter group more exploratory than definitive.

# 6 References

-   [Codebook of the Dataset](https://data.mendeley.com/datasets/23ppcdbmhc/1)
